---
title: "Untitled"
author: "Brigitte Hogan"
date: "3/11/2019"
output: 
  html_document: 
    fig_caption: yes
    toc: yes
    keep_md: yes
---

# Introduction

Here is my first RMarkdown document.

# Let's embed some R code

We'll write an R chunk here that loads the tidyverse library and then reads in the gapminder dataset from our project directory.  

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
gm <- read_csv("gapminder.csv")
```

# Investigate gm

Let's look at the gm dataset

```{r}
head(gm)
```

# Our first plot

Showing the GDP per capita on the x-axis and the life expectancy on the y-axis

```{r}
gm %>%
  ggplot(aes(gdp_per_cap, lifeexp)) +
  geom_point()
```

# A better plot

Adding color by continent and adding a log scale for GDP

```{r, fig.cap="Life Expectancy by log GDP"}
gm %>%
  ggplot(aes(gdp_per_cap, lifeexp)) +
  scale_x_log10() +
  geom_point(aes(col=continent))
```

# Option 1

Trying chunk option "Echo = False"

```{r, fig.cap="Life Expectancy by log GDP", echo=FALSE}
gm %>%
  ggplot(aes(gdp_per_cap, lifeexp)) +
  scale_x_log10() +
  geom_point(aes(col=continent))
```

# Option 2

Trying chunk option "fig.show = hide"

```{r, fig.cap="Life Expectancy by log GDP", fig.show="hide"}
gm %>%
  ggplot(aes(gdp_per_cap, lifeexp)) +
  scale_x_log10() +
  geom_point(aes(col=continent))
```

# Option 3

Trying chunk option "include = FALSE"

```{r, fig.cap="Life Expectancy by log GDP", include=FALSE}
gm %>%
  ggplot(aes(gdp_per_cap, lifeexp)) +
  scale_x_log10() +
  geom_point(aes(col=continent))
```


# Kable Table

Trying a simple table

```{r}
head(gm)
```

head as a table
```{r}
library(knitr)
kable(head(gm))
```

